The Near and Mid-infrared photometric properties of known redshift $z\geq5$ Quasars

### 2020-01-13 tex/MNRAS_submission/rv1/VHzQ_MNRAS_rv1.tex
Updated with new database name

The data are on the WFCAM Science Archive: \href{wsa.roe.ac.uk}{\tt wsa.roe.ac.uk}. 
Access the User Login form \href{WFCAM Science Archive}{\tt wsa.roe.ac.uk/login.html} 
with these credentials::
\begin{itemize}
    \item Username: {\tt WSERV1000} 
    \item password: {\tt highzqso} 
    \item community: {\tt nonsurvey}
\end{itemize}
Then going to the
\href{http://wsa.roe.ac.uk:8080/wsa/SQL_form.jsp}{{\tt Free Form SQL
Query}} page the Database release {\tt WSERV1000v20190507} can be
accessed which contains all the data we use here.

@@

At the \href{http://horus.roe.ac.uk/vsa/login.html}{VSA Login}, enter 
with these credentials::
\begin{itemize}
    \item Username: {\tt VSERV1000} 
    \item password: {\tt highzqso} 
    \item community: {\tt proprietary}
\end{itemize}
Then the \href{http://horus.roe.ac.uk:8080/vdfs/VSQL_form.jsp}{Freeform SQL
Query} page is where the database release to use is {\tt
VSERV1000v20190508}. The queries are the same as those used in the
WSA, see Appendix~\ref{sec:SQL_WSA}, but the names of the tables starting
with {\tt wserv1000} should be replaced with {\tt vserv1000}.

>>>>

The data are on the WFCAM Science Archive: \href{wsa.roe.ac.uk}{\tt wsa.roe.ac.uk}. 
Access the User Login form \href{WFCAM Science Archive}{\tt wsa.roe.ac.uk/login.html} 
with these credentials::
\begin{itemize}
    \item Username: {\tt WSERV1000} 
    \item password: {\tt highzqso} 
    \item community: {\tt nonsurvey}
\end{itemize}
Then going to the
\href{http://wsa.roe.ac.uk:8080/wsa/SQL_form.jsp}{{\tt Free Form SQL
Query}} page the Database release {\tt WSERV1000v20200113} can be
accessed which contains all the data we use here.

@@

At the \href{http://horus.roe.ac.uk/vsa/login.html}{VSA Login}, enter 
with these credentials::
\begin{itemize}
    \item Username: {\tt VSERV1000} 
    \item password: {\tt highzqso} 
    \item community: {\tt proprietary}
\end{itemize}
Then the \href{http://horus.roe.ac.uk:8080/vdfs/VSQL_form.jsp}{Freeform SQL
Query} page is where the database release to use is {\tt
VSERV1000v20200113}. The queries are the same as those used in the
WSA, see Appendix~\ref{sec:SQL_WSA}, but the names of the tables starting
with {\tt wserv1000} should be replaced with {\tt vserv1000}.
